Discussion Draft

### 2020-03-18 doc/Discussion.rmd
trying to force writing

@@

This section refers to the matrix of models and results from this study where we (conceptually test if each model would support our results). We were motivated to run a comparison of

## 1.Gamete selection

The process where gametes are competing - so there is stronger selection for 1 form of gamete vs the other (stronger directional selection) (the gamete with more competition / the sex with more variance in reproductive fitness will have lower overall recombination rate.

<go through the squares>

this is a modifer model it abstracts the genome area.

@@

@@

## 2. SACE

@@

## 3.Two-locus (protect for drivers)

@@

## 4. Segregation and physiological Spindle Differences

>>>>

#imortant of testable hypotheses

#model not included in this comparison

@@

In our analysis / synthesis of results, we decded to test and systematically compared models which have been proposed to explain our results (both for the sex dfferences and the faster male evolution of recombination rates).  We attempted to test the hypotheses of if our choosen models could produce the main / general patterns oberved in this study (Table X)

We generall focus on models for the evolution of heterochiasmy since that is the primary data/set of results in this study. We search for a parsimonius explanation /model that fits both the results from sex differences and the faster male evolution.

# 1.Gamete selection

originally proposed/outlined by Trivers [] and refined /formatlized in [@lenormand2003]. This model discribes a system where gametes are competing or selection is acting in the haploid stage to cause difference in genome wide recombiaion rates between males and females.

 This is a modefier model of three loci, where the recombination rate between two loci is determined by a third locus (or modifer).

@@

<the sex with the most variable reproductive fitness will be selected to have lower genome wide recombination rates>

From our results, this model would predict -- fit the results of:

@@

# 2. SACE

@@

# 3.Two-locus (protect for drivers)

@@

# 4. Segregation and physiological Spindle Differences
